ropenblas: Download, Compile and Link OpenBLAS Library with R

### 2021-03-22 paper/paper.Rmd
Update

```{r bench, echo = FALSE, fig.cap = "Benchmarks of a decomposition of singular and inverse value of a matrix of dimension 1000 x 1000.", fig.align = "center", out.width="65%"}
knitr::include_graphics(path = "benchmark.png") 
```

>>>>

```{r bench, echo = FALSE, fig.cap = "Benchmarks of a decomposition of singular and inverse value of a matrix of dimension 1000 x 1000.", fig.align = "center", out.width="60%"}
knitr::include_graphics(path = "benchmark.png") 
```
